Textmining in Economics

### 2017-10-13 textm.Rmd
more

  - E.g.: Principal Component Analysis, latent Dirichlet Allocation

>>>>

  - E.g.: Principal Component Analysis, Topic Modeling (latent Dirichlet Allocation)

# Topic Modeling
## Topic Modeling

method for finding a group of words (i.e topic) from a collection of documents that best represents the information in the collection.

  - Discovering hidden topical patterns that are present across the collection
  - Annotating documents according to these topics
  - Using these annotations to organize, search and summarize texts

There are many techniques that are used to obtain topic models: Latent Dirichlet allocation

## Latent Dirichlet Allocation (LDA)

consider the following set of documents as the corpus:
```{r}
doc1 <- "I had a peanut butter sandwich for breakfast"
doc2 <- "I like to eat almonds, peanut and walnuts."
doc3 <- "My neighbor got a little dog yesterday."
doc4 <- "Cats and dogs are mortal enemies."
doc5 <- "You must not feed peanuts to your dog."
```

This gives the following Document-Term-Matrix
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tm)

# Build corpus 
corpus <- rbind(doc1, doc2, doc3, doc4, doc5)

# clean corpus
corpus <- tolower(corpus)
corpus <- removeWords(corpus, stopwords("english"))
corpus <- gsub( "[^[:alnum:]]", " ", corpus)
corpus <- gsub("^\\s+|\\s+$", "", corpus)

#Create document-term matrix
dtm <- Corpus(VectorSource(corpus))
dtm <- DocumentTermMatrix(dtm)

inspect(dtm)
```

***
Now we set the model parameter

```{r, include=FALSE}
library(lda)

corpusLDA <- lexicalize(corpus)
```

```{r, echo=FALSE}
ldaModel <- lda.collapsed.gibbs.sampler(corpusLDA$documents,K=2,vocab=corpusLDA$vocab,burnin=9999,num.iterations=100000,alpha=0.8,eta=0.1)

top.words <- top.topic.words(ldaModel$topics, 3, by.score=TRUE)
print(top.words)
```
